\textbf{{\LaTeX} template for the QITL5 abstract \\ Leuven, Sept. 12-14, 2013}

### 2015-10-05 writing/S'15 LSTM/data.tex
Paper work

\begin{table}[tp]
  \centering\small
%  \begin{subtable}[t]{0.45\textwidth}
%    \centering
%    \begin{tabular}[t]{l l}
%      \toprule
%      Formula     & Interpretation \\
%      \midrule
%      $p_1$, $p_2$, $p_3$, $p_4$, $p_5$, $p_6$ & $\sem{x} \in \{\True, \False\}$ \\
%      $\plneg \varphi$ & $\True$ iff $\sem{\varphi} = \False$ \\
%      $(\varphi \pland \psi)$ & $\True$ iff $\False \notin \{\sem{\varphi}, \sem{\psi}\}$ \\
%      $(\varphi \plor \psi)$  & $\True$ iff $\True \in \{\sem{\varphi}, \sem{\psi}\}$ \\
%      \bottomrule
%    \end{tabular}    
%    \caption{Well-formed formulae. $\varphi$ and $\psi$
%      range over all well-formed formulae, and $\sem{\cdot}$ is
%      the interpretation function mapping formulae into $\{\True,
%      \False\}$.}\label{tab:pl}
%  \end{subtable}
    \begin{tabular}[t]{r c l}
      \toprule
      $\plneg p_3$        & $\natneg$ & $p_3$ \\
%      $\plneg \plneg p_6$ & $\nateq$  & $p_6$ \\
      $p_3$               & $\natfor$ & $p_3 \plor p_2$ \\
%      $p_1 \plor (p_2 \plor p_4)$               & $\natrev$ & $p_2 \pland  \plneg p_4$ \\
      $(\plneg p_2) \pland p_6  $ & $\natalt$ & $     \plneg ( p_6 \plor ( p_5 \plor p_3 ) ) $\\
      %$(a \natfor b)$   & $\nateq$  & $(b \natrev a)$ \\	
 $    p_4 \plor ( \plneg ( ( p_1   $ & $ \natfor $ & $  \plneg ( ( ( ( \plneg p_6 ) \plor ( \plneg p_4 ) )   $\\      
$ \plor p_6 )  \plor p_4 ) )$ &&$ \pland ( \plneg p_5 ) )\pland ( p_6 \pland p_6 ) ) $\\
% $(p_3 \pland \plneg p_1 ) \plor \plneg p_3$    & $\natrev$& $\plneg\, (p_3 \plor p_2)$ \\
      %<	( not ( c ( or b ) ) )	( ( c ( and ( not a ) ) ) ( or ( not c ) ) )
      \bottomrule
    \end{tabular}
    \caption{Examples of short to moderate length pairs from the artificial data introduced by \protect\citealt{Bowman:Potts:Manning:2014}. For brevity, we only show the parentheses that are needed to disambiguate the sentences rather than the full binary bracketings.}\label{tab:plexs}
\end{table}

>>>>

\begin{table}[tp]
  \centering\small
%  \begin{subtable}[t]{0.45\textwidth}
%    \centering
%    \begin{tabular}[t]{l l}
%      \toprule
%      Formula     & Interpretation \\
%      \midrule
%      $p_1$, $p_2$, $p_3$, $p_4$, $p_5$, $p_6$ & $\sem{x} \in \{\True, \False\}$ \\
%      $\plneg \varphi$ & $\True$ iff $\sem{\varphi} = \False$ \\
%      $(\varphi \pland \psi)$ & $\True$ iff $\False \notin \{\sem{\varphi}, \sem{\psi}\}$ \\
%      $(\varphi \plor \psi)$  & $\True$ iff $\True \in \{\sem{\varphi}, \sem{\psi}\}$ \\
%      \bottomrule
%    \end{tabular}    
%    \caption{Well-formed formulae. $\varphi$ and $\psi$
%      range over all well-formed formulae, and $\sem{\cdot}$ is
%      the interpretation function mapping formulae into $\{\True,
%      \False\}$.}\label{tab:pl}
%  \end{subtable}
    \begin{tabular}[t]{r c l}
      \toprule
      $\plneg p_3$        & $\natneg$ & $p_3$ \\
%      $\plneg \plneg p_6$ & $\nateq$  & $p_6$ \\
      $p_3$               & $\natfor$ & $p_3 \plor p_2$ \\
%      $p_1 \plor (p_2 \plor p_4)$               & $\natrev$ & $p_2 \pland  \plneg p_4$ \\
      $(\plneg p_2) \pland p_6  $ & $\natalt$ & $     \plneg ( p_6 \plor ( p_5 \plor p_3 ) ) $\\
      %$(a \natfor b)$   & $\nateq$  & $(b \natrev a)$ \\	
 $    p_4 \plor ( \plneg ( ( p_1   $ & $ \natfor $ & $  \plneg ( ( ( ( \plneg p_6 ) \plor ( \plneg p_4 ) )   $\\      
$ \plor p_6 )  \plor p_4 ) )$ &&$ \pland ( \plneg p_5 ) )\pland ( p_6 \pland p_6 ) ) $\\
% $(p_3 \pland \plneg p_1 ) \plor \plneg p_3$    & $\natrev$& $\plneg\, (p_3 \plor p_2)$ \\
      %<	( not ( c ( or b ) ) )	( ( c ( and ( not a ) ) ) ( or ( not c ) ) )
      \bottomrule
    \end{tabular}
    \caption{Examples of short to moderate length pairs from the artificial data introduced in \protect\citealt{Bowman:Potts:Manning:2014}. We only show the parentheses that are needed to disambiguate the sentences rather than the full binary bracketings.}\label{tab:plexs}
\end{table}

### 2015-10-05 writing/SNLI paper/arxiv_package/abstract.tex
Paper work

\begin{abstract} 
Understanding entailment and contradiction is  fundamental to understanding natural language, and inference about entailment and contradiction is a valuable testing ground for the development of semantic representations. However, machine learning research in this area has been dramatically limited by the lack of large-scale resources. To address this, we introduce the Stanford Natural Language Inference corpus, a new freely available collection of labeled sentence pairs, written by humans doing a novel grounded task based on image captioning. At 570K pairs, it is two orders of magnitude larger than all other resources of its type. We find that this increase in scale allows lexicalized classifiers to outperform some sophisticated existing entailment models, and that it allows a neural network-based model to perform competitively on natural language inference benchmarks for the first time.
\end{abstract}

>>>>

\begin{abstract} 
Understanding entailment and contradiction is  fundamental to understanding natural language, and inference about entailment and contradiction is a valuable testing ground for the development of semantic representations. However, machine learning research in this area has been dramatically limited by the lack of large-scale resources. To address this, we introduce the Stanford Natural Language Inference corpus, a new, freely available collection of labeled sentence pairs, written by humans doing a novel grounded task based on image captioning. At 570K pairs, it is two orders of magnitude larger than all other resources of its type. This increase in scale allows lexicalized classifiers to outperform some sophisticated existing entailment models, and it allows a neural network-based model to perform competitively on natural language inference benchmarks for the first time.
\end{abstract}

### 2015-10-05 writing/SNLI paper/arxiv_package/entailment_eval.tex
Paper work

The most immediate application for our corpus is in developing models for the task of NLI\@. In particular, since it is dramatically larger than any existing corpus of comparable quality, we expect it to be suitable for training parameter-rich models like neural networks, which have not previously been competitive at this task. In this section, we explore the performance of three classes of models: (i)~models from a well-known NLI system, the Excitement Open Platform; (ii)~variants of a strong but simple feature-based classifier model, which makes use of both unlexicalized and lexicalized features, and (iii)~distributed representation models, including a baseline model and neural network sequence models.

@@

The first class of models is from the Excitement Open
  Platform (EOP,
  \citealt{pado2014design,magnini2014excitement})---an open source platform for RTE research.
%  which
%  is distributed alongside a number of RTE pipelines.
%
% what is EOP
EOP is a tool for quickly developing NLI systems
  while sharing components such as common lexical resources and 
  evaluation sets.
We evaluate on two algorithms included in the distribution:
%  and also evaluated in \newcite{magnini2014excitement}.
%These are: 
  a simple edit-distance based algorithm and
  a classifier-based algorithm.
%  (3) an algorithm based around tree transformations.

>>>>

The most immediate application for our corpus is in developing models for the task of NLI\@. In particular, since it is dramatically larger than any existing corpus of comparable quality, we expect it to be suitable for training parameter-rich models like neural networks, which have not previously been competitive at this task. Our ability to evaluate standard classifier-base NLI models, however, was limited to those which were designed to scale to SNLI's size without modification, so a more complete comparison of approaches will have to wait for future work. In this section, we explore the performance of three classes of models which could scale readily: (i)~models from a well-known NLI system, the Excitement Open Platform; (ii)~variants of a strong but simple feature-based classifier model, which makes use of both unlexicalized and lexicalized features, and (iii)~distributed representation models, including a baseline model and neural network sequence models.

@@

The first class of models is from the Excitement Open
  Platform (EOP,
  \citealt{pado2014design,magnini2014excitement})---an open source platform for RTE research.
%  which
%  is distributed alongside a number of RTE pipelines.
%
% what is EOP
EOP is a tool for quickly developing NLI systems
  while sharing components such as common lexical resources and 
  evaluation sets.
We evaluate on two algorithms included in the distribution:
  a simple edit-distance based algorithm and
  a classifier-based algorithm, the latter both in a bare form and augmented 
  with EOP's full suite of lexical resources.
%  (3) an algorithm based around tree transformations.

### 2015-10-05 writing/SNLI paper/arxiv_package/intro.tex
Paper work

Our ultimate objective in this paper is to provide an empirical
evaluation of learning-centered approaches to NLI with a focus on
systems for representation learning,
advancing the case for NLI as a tool for the evaluation of 
domain-general approaches to semantic representation. 
However, in our view, existing NLI corpora do not
permit such an assessment. They are generally too small for training
modern data-intensive, wide-coverage models, many contain sentences
that were algorithmically generated, and they are often beset with
indeterminacies of event and entity coreference that significantly
impact annotation quality.

>>>>

Our ultimate objective is to provide an empirical
evaluation of learning-centered approaches to NLI,
advancing the case for NLI as a tool for the evaluation of 
domain-general approaches to semantic representation. 
However, in our view, existing NLI corpora do not
permit such an assessment. They are generally too small for training
modern data-intensive, wide-coverage models, many contain sentences
that were algorithmically generated, and they are often beset with
indeterminacies of event and entity coreference that significantly
impact annotation quality.

### 2015-10-05 writing/SNLI paper/arxiv_package/model_structure_fig.tex
Paper work

        \caption{The classification architecture used in all NLI evaluations: for each sentence embedding model evaluated in \reftabs{tab:nnresults}{tab:transferresults}, two identical copies of the model are run with the two sentences as input, and their outputs are used as the two 100d inputs shown here.}
  \label{modelstructure}
\end{figure}

>>>>

        \caption{The neural network classification architecture: for each sentence embedding model evaluated in \reftabs{tab:nnresults}{tab:transferresults}, two identical copies of the model are run with the two sentences as input, and their outputs are used as the two 100d inputs shown here.}
  \label{modelstructure}
\end{figure}
